---
title: "L1P2"
author: "Rafael Falcão"
output:
  prettydoc::html_pretty:
    df_print: kable
    theme: cayman
    highlight: github
---

<style>
body {
text-align: justify}
</style>

```{r setup}
library(tidyverse)
library(here)
library(lubridate)
theme_set(theme_bw())
```

```{r ETL}
buscas = read_csv(here::here("data/search_data.csv"))
```

What is our daily overall clickthrough rate? How does it vary between the groups?

```{r}
buscas %>%
    group_by(date = substr(session_start_date, 1, 10), group) %>%
    summarise(click_mean = mean(num_clicks)) %>%
    ggplot(aes(x = date, y = click_mean, color = group, group = group)) +
    geom_point() +
    geom_line() +
    facet_grid(~group) +
    labs(y = "Click Mean", x = "") +
    labs(title = "Daily Overall Rate") + 
    theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(hjust = 1, angle = 45), legend.position="none")
```

Which results do people tend to try first? How does it change day-to-day?

```{r}
buscas %>%
    filter(first_click < 21) %>%
    ggplot(aes(x = first_click)) +
    geom_bar(fill = "#FF6666") +
    labs(y = "Count First Click", x = "First Click") +
    labs(title = "Results that people tend to try first")

# Explicar cauda no texto
# first_click tende a 20 por causa do número de resultados por página (20).
``` 

```{r}
# Fazer isso para cada dia para mostrar o 90 percentil de cada dia.
buscas %>%
    group_by(date = substr(session_start_date, 1, 10)) %>%
    filter(date == "2016-03-01") %>%
    summary(first_click)

buscas %>%
    group_by(date = substr(session_start_date, 1, 10)) %>%
    filter(date == "2016-03-02") %>%
    summary(first_click)
    
``` 

What is our daily overall zero results rate? How does it vary between the groups?

```{r}

buscas %>%
    group_by(date = substr(session_start_date, 1, 10), group) %>%
    summarise(count_zero = sum(results == 0), total = n()) %>%
    ggplot(aes(x = date, y = count_zero/total , color = group, group = group)) +
    geom_point() + 
    geom_line() +
    facet_grid(~group) +
    labs(y = "Zero Results Overall", x = "") +
    labs(title = "Daily Overall Zero Results Rate") + 
    theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(hjust = 1, angle = 45), legend.position="none")

```

Let session length be approximately the time between the first event and the last event in a session. Choose a variable from the dataset and describe its relationship to session length. Visualize the relationship.

```{r}
# Testar a relação de 'session_length' com cada variavel.
```

Summarize your findings in an executive summary.

```{r}

```
